---
title: "Project01Task04"
execute: 
  keep-md: True
format: 
  html: 
    code-fold: true
    code-line-numbers: true
editor: visual
---

## Introduction

We are using the different functions to fit our models of the light bulb dataset and we are going to find where our model will be at 80% of the initial intensity.

```{r}
library(data4led)
library(ggplot2)
library(tidyverse)
bulb <- led_bulb(1,seed = 5372)
x <- seq(-10,80000,2)
t <- bulb$hours
y1 <- bulb$percent_intensity
```

\## Function 0

As we can see from the figure below, f(t) = 100 with t\>= 0 we set the t = 0 to make sure that the light bulbs intensity is at 100% when turned on. The horizontal line represents the bulb at 100% intensity. We can see that our model will never hit 80% intensity.

```{r}
f0 <- function(t,a0=0){ a0 + t*0 }
y0 <- f0(x,a0=100)
uniroot(f0,c(0,80))$root
par(mfrow=c(1,2),mar=c(2,2,3,0.25),oma=rep(0.5,4))
plot(t,y1,xlab="Hour ", ylab="Intensity(%) ", pch=16,main='f0', ylim = c(99.5, 102))
lines(x,y0,col=2)
plot(t,y1,xlab="Hour ", ylab="Intensity(%) ", pch=16, xlim = c(-10,80000),ylim = c(-10,120))
lines(x,y0,col=2)
```

\## Function 1

The function below shows the plot where f(t)=100 with t \>= 0. We can see that the parameter is at a0 = 100 and it increases over time with a1 = 0.00011. We can see that this function will also never reach 80% intensity because the model will never go back down from the initial intensity.

```{r}
f1 <- function(t,a0=0,a1=0){ a0 + a1*t }
y11 <- f1(x,a0=80,a1=0.00011)

uniroot(f1, c(0,80 ))$root

par(mfrow=c(1,2),mar=c(2,2,3,0.25),oma=rep(0.5,4))
plot(t,y1,xlab="Hour ", ylab="Intensity(%) ", pch=16,main='f1', ylim = c(99.5, 102))
lines(x,y11,col=2)
plot(t,y1,xlab="Hour ", ylab="Intensity(%) ", pch=16, xlim = c(-10,80000),ylim = c(-10,120))
lines(x,y11,col=2)
```

\## Function 2

With the function below we see that a0 = 100, a1 = .0055, a2 = -0.000005. This function matches the graph very poorly because it increases at a short time and drops fast within a short time which does not match our points.

```{r}
f2 <- function(t,a0=100,a1=0.0009,a2=-0.00000017){ a0 + a1*t + a2*t^2 }
y2 = f2(x,a0=100,a1=0.0009,a2=-0.00000017)

my_root <- uniroot(f2, c(1,80000))$root
par(mfrow=c(1,2),mar=c(2,2,3,0.25),oma=rep(0.5,4))
plot(t,y1,xlab="Hour ", ylab="Intensity(%) ", pch=16,main='f2', ylim = c(99.5, 102))
lines(x,y2,col=2)
plot(t,y1,xlab="Hour ", ylab="Intensity(%) ", pch=16, xlim = c(-10,80000),ylim = c(-10,120))
lines(x,y2,col=2)
abline(h=80,col = "gray")
abline(v=my_root,col = "gray")
points(my_root,80, col = "red")
```
